Examining a Quarter Century of Publishing Trends in Social Work Research:

### 2015-04-08 manuscript.Rmd
Removed hard coding from analysis.

```{r warning=FALSE, message=FALSE, eval=TRUE}
# Clear workspace
rm(list=ls())

@@

@@

#load("/Users/beperron/Git/SocialWorkResearch/socialWorkHistory.Rdata")

@@

```{r imageMaker, comment=NA, echo=FALSE, eval=TRUE}
# Read data files
load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoFULL.R")
load("/Users/beperron/Git/SocialWorkResearch/Data/proQuest.R")
hodge <- readLines("/Users/beperron/Git/SocialWorkResearch/search_specifications/hodge.txt", n = -1)

source("/Users/beperron/Git/SocialWorkResearch/functions/combineData.R")
source("/Users/beperron/Git/SocialWorkResearch/functions/cleaningJournals.R")
source("/Users/beperron/Git/SocialWorkResearch/functions/shortArticlesRevised.R")
source("/Users/beperron/Git/SocialWorkResearch/functions/titleMatching.R")
source("/Users/beperron/Git/SocialWorkResearch/functions/otherDocuments.R")
source("/Users/beperron/Git/SocialWorkResearch/functions/fewArticles.R")
source("/Users/beperron/Git/SocialWorkResearch/functions/pretty.R")

combineData.f()
cleaningJournals.f()
shortArticles.f()
titleMatching.f()
otherDocuments.f()
fewArticles.f()
#save.image(file = "socialWorkHistory.Rdata")
```

>>>>

```{r objectMakerProQuest, warning=FALSE, message=FALSE, eval=FALSE, results='hide'}
# Clear workspace
rm(list=ls())

@@

```{r objectMakerEbscoHost,warning=FALSE, message=FALSE, eval=FALSE, results='hide'}
# Clear workspace
rm(list=ls())

# Read BWR functions for Mac OS
source("/Users/beperron/Git/BibWrangleR/functions/ebscoBWR.R")

# Set the working directory to store files created by BWR functions
path <- "/Users/beperron/Git/SocialWorkResearch/Data/ebscoFULL"

ebscoBWR.f(csv=FALSE, path=path)
save(ebscoBWR.df, file = "ebscoFULL.R")
```

@@

load("/Users/beperron/Git/SocialWorkResearch/socialWorkHistory.Rdata")

@@

```{r imageMaker, comment=NA, echo=FALSE, eval=FALSE}
# Read data files
load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoFULL.R")
load("/Users/beperron/Git/SocialWorkResearch/Data/proQuest.R")
hodge <- readLines("/Users/beperron/Git/SocialWorkResearch/search_specifications/hodge.txt", n = -1)

#source("/Users/beperron/Git/SocialWorkResearch/functions/combineData.R")
#source("/Users/beperron/Git/SocialWorkResearch/functions/cleaningJournals.R")
#source("/Users/beperron/Git/SocialWorkResearch/functions/shortArticlesRevised.R")
#source("/Users/beperron/Git/SocialWorkResearch/functions/titleMatching.R")
#source("/Users/beperron/Git/SocialWorkResearch/functions/otherDocuments.R")
#source("/Users/beperron/Git/SocialWorkResearch/functions/fewArticles.R")
#source("/Users/beperron/Git/SocialWorkResearch/functions/pretty.R")

#combineData.f()
#cleaningJournals.f()
#shortArticles.f()
#titleMatching.f()
#otherDocuments.f()
#fewArticles.f()
#save.image(file = "socialWorkHistory.Rdata")
```
